Classless Java

### 2015-09-13 paper/paper.tex
Split tex into files. Text for comparison,

\section{Introduction}\label{sec:intro}

\begin{itemize}

\item Using annotattions to implement a rich notion of traits with a 
mechanism to instantiate objects (the of method). Goal 1: is to reduce 
the amount of code that is required to program with interfaces and default 
methods. Goal 2: To provide a convenient means to do multiple inheritance 
in Java.

\item Specify the system more formally.

\item Show that we can model all trait operations

\item Implementation using Lombok

\item Case studies: The expression problem, Trivially
Case Studies from traits paper.

\end{itemize}

\section{Overview}\label{sec:ep}
Yanlin

* Explain what the Mixin annotations do using examples.

* Motivate the use of multiple inheritance in Java.

* Maybe use Marco's example (Point example).

\lstinputlisting[linerange=33-42]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINT

\lstinputlisting[linerange=48-74]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINT_OF

\section{Comparing to traits and mixins}
Haoyuan

   - vs both: we do automatic return type refinement, which has useful applications 
   (example: Expression Problem)

   - vs traits: we support of methods to create new objects (a replacement to constructors);
   Moreover we have the with and clone methods (we miss more applications for those). Show 
   how to model the operations on traits; discuss operations that we cannot model 
   (example: renaming).

   - vs mixins: we use the trait model of explicitly resolving conflicts. This is arguably 
   better for reasoning.

\section{Formal Semantics}\label{sec:typesafety}
Yanlin and Haoyuan

We need to show 2 things:

1) The dynamic semantics: what's the code that gets generated by a mixin annotation;

2) The type system: what programs to reject; properties: generation of type-safe/checkable code.

\bruno{The implementation is still missing the type system (rejecting some programs)!}

\section{Implementation}
Haoyuan

discuss implementation in lombok; and limitations.

\bruno{The implementation does not support separate compilation yet. Can we fix this?}

\section{Case studies}
Haoyuan and Yanlin

\subsection{A Trivial Solution to the Expression Problem}

\subsection{Other case studies} 
\bruno{The case studies still need to be implemented!}

Collections example from traits paper?

Other case studies using multiple inheritance?

\section{Related Work}\label{sec:related}

- traits (original, variations, scala)
- mixins (original, scala)
- multiple inheritance 
- expression problem
- ...

%===============================================================================
\section{Conclusion}\label{sec:conclusion}

>>>>

\input{sections/Introduction.tex}

\input{sections/Overview.tex}

\input{sections/Compare.tex}

\input{sections/Formalization.tex}

\input{sections/Implementation.tex}

\input{sections/CaseStudy.tex}

\input{sections/RelatedWork.tex}

%===============================================================================
\input{sections/Conclusion.tex}
